---
title: "P8105 Data Science I Homework 1"
author: Olivia Wang (hw2852)
output: github_document
date: "2022-09-17"
---

# Problem 1

## Loading & Summarizing the `Penguins` Dataset
First, let us load the `penguins` dataset.

```{r}
data("penguins", package = "palmerpenguins")
```

Next, let us generate a summary of the `penguins` dataset, as well as determine the number of rows and columns in the dataset. 
```{r}
summary(penguins)
nrow(penguins)
ncol(penguins)
```
Dataset `penguins` has **344 rows** and **8 columns**. The 8 rows each represent the following variables:

1. Species: Adelie, Chinstrap, Gentoo
1. Island: Biscoe, Dream, Torgersen
1. Bill length in mm: 32.10 to 59.60
1. Bill depth in mm: 13.10 to 21.50
1. Flipper length in mm: 172.0 to 231.0
1. Body mass in g: 2700 to 6300
1. Sex: Female, Male
1. Year: 2007, 2008, 2009

Based on the summary of the `penguins` dataset, we can see that the mean flipper length is **200.9mm**.

## Scatterplotting Flipper Length vs. Bill Length

Let us generate a scatterplot, plotting flipper length vs. bill length, both measured in mm, using `ggplot`.
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point(na.rm = TRUE)
```


