---
title: "P8105 Data Science I Homework 1"
author: Olivia Wang (hw2852)
output: github_document
date: "2022-09-17"
---

# Problem 1

## Loading & Summarizing the `Penguins` Dataset
First, let us load the `penguins` dataset.

```{r}
data("penguins", package = "palmerpenguins")
```

Next, let us generate a summary of the `penguins` dataset, as well as determine the number of rows and columns in the dataset. 
```{r}
summary(penguins)
nrow(penguins)
ncol(penguins)
```
Dataset `penguins` has **344 rows** and **8 columns**. The 8 rows each represent the following variables:

1. Species: Adelie, Chinstrap, Gentoo
1. Island: Biscoe, Dream, Torgersen
1. Bill length in mm: 32.10 to 59.60
1. Bill depth in mm: 13.10 to 21.50
1. Flipper length in mm: 172.0 to 231.0
1. Body mass in g: 2700 to 6300
1. Sex: Female, Male
1. Year: 2007, 2008, 2009

Based on the summary of the `penguins` dataset, we can see that the mean flipper length is **200.9mm**.

## Scatterplotting Flipper Length vs. Bill Length

Let us generate a scatterplot, plotting flipper length vs. bill length, both measured in mm, using `ggplot`. In order to use the `ggplot` function, let us first load the `tidyverse` library.
```{r}
library(tidyverse)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point(na.rm = TRUE)
```

We can now export the scatterplot generated above to the project directory using the `ggsave` function. 
```{r}
ggsave("penguins_flipper_vs_bill_scatterplot.pdf")
```

# Problem 2

## Creating a Dataframe

First, let us create a dataframe comprised of:

* A random sample of size 10 from a standard Normal distribution;
* A logical vector indicating whether elements of the sample are greater than 0;
* A character vector of length 10; and
* A factor vector of legnth 10, with 3 different factor "levels".

```{r}
problem2_df = 
  tibble(
    var_numeric = rnorm(n = 10, mean = 0, sd = 1),  
    var_logic = c(var_numeric > 0), 
    var_character = c("cat", "dog", "goat", "cow", "elephant", "sheep", "horse", "koala", "pig", "flamingo"), 
    var_factor = factor(c("high", "medium", "low", "low", "high", "low", "medium", "high", "low", "medium"))
    )
```

Next, let us try to take the mean of each variable in the `problem2` dataframe.

```{r}
mean(pull(.data = problem2_df, var = var_numeric))
mean(pull(.data = problem2_df, var = var_logic))
mean(pull(.data = problem2_df, var = var_character))
mean(pull(.data = problem2_df, var = var_factor))
```




